\documentclass{article}
% :autocmd BufWritePost notes.tex call Tex_RunLaTeX()
\usepackage[]{amsmath}
\usepackage[]{hyperref}
\title{Elevator Scheduling}
\author{Robert Foy}
\date{ }

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
This project is an experimentation around appraising different elevator scheduling algorithms.

\section{Existing Algorithms}
\begin{itemize}
   \item Nearest Car \hfill \\
   Assign the elevator best placed to answer the call, based on a Figure of Suitability (FS).
   The figure of suitability is derived from three criteria:
   \begin{enumerate}
      \item $E \rightarrow C_{F} \land C_{D} = E{_D} \iff FS = (N + 2) - d$
      \item $E \rightarrow C_{F} \land C_{D} = \neg E_{D} \iff FS = (N + 1) -d$
      \item $E \leftarrow C_{F} \iff FS = 1$
   \end{enumerate}
   Where:
   \begin{align*}
      &E \rightarrow C_{F} = \text{Elevator is moving towards the caller} \\
      &E \leftarrow C_{F} = \text{Elevator is moving away from the caller} \\
      &C_{D} = \text{Caller Direction} \\
      &E_{D} = \text{Elevator Direction} \\
      &FS = \text{Figure of Suitability} \\
      &N = \text{Number of floors} \\
      &d = \text{Difference in floors between elevator location and the current caller}
   \end{align*}
   \item Fixed Sector Common Sector System (FSO) \hfill \\
   Building is divided into sectors, one for search elevator. Elevators preferentially serve their own sector.
   \item Fixed Sectoring Priority Timed System (FS4) \hfill \\
   Building is divided into up sectors and down sectors. Elevators only act in their up-down sectors.
   \item Dynamic Sectoring System  \hfill \\
   Floors are grouped into dynamic sectors, which are assigned to elevators. The sectors are allocated based on their size and location.
\end{itemize}

\section{Ideas to Explore}
\begin{itemize}
   \item DSL to Represent the Scheduling Algorithm
   \item Potential for Memoryless Implementation
   \item Genetic algorithms
   \item Encoding as cellular automata
\end{itemize}

\section{Code Entities}
\begin{itemize}
  \item Lifts
  \item People
\end{itemize}

\section{Code Structure}
All source code is contained under the /src folder.
Utilities are contained under /src/lib.

\section{Unit Testing Libraries}
For unit testing, \href{http://cutest.sourceforge.net/}{CuTest} is being utilized.

\end{document}
